Multi-Agent Reinforcement Learning in Zombie-Survival Games

### 2020-12-18 paper/paper.tex
update paper

%
% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

@@

In the \emph{anonymity} scenario we modify the \emph{baseline} scenario to introduce partial observability.
We re-order agents' state vectors each step so that agents within teams are ordered by distance to the observing agent.
To a survivor, a zombie now appears the same as any other zombie, and does not have identity by virtue of index in the state vector.
We expect both survivors and zombies to learn more general policies with faster convergence than the baseline.

>>>>

% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}

\renewcommand{\UrlFont}{\ttfamily\small}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/baseline_reward.png}
  \caption{Reward (moving average over 100 episodes) for survivors (green) and zombies (red) for 10 training runs.}
  \label{fig:baseline_reward}
\end{figure}

There was some variability between training runs in the baseline scenario.
Figure \ref{fig:baseline_reward} shows agent reward graphs over multiple runs.
The reward trace for $r_5$ shows the zombie agent experienced a spike in reward corresponding to a drop in reward for a survivor in $r_0$
that occurred only once in 10 training runs.
Most agents show a similar pattern for at least one run.

On further investigation we discovered the reason for this; a zombie usually fixates on a target, but zombies learn policies at different rates.
Figure \ref{fig:baseline_speed} shows speed and reward over time for a single training run.
We see that one survivor is not pursued as often to start with, but then recieves increasing attention from zombies learning to persure it.
Following this attention the survivor learns to move much faster.
We observed similar patterns in other runs.

In the baseline state-space, every agent is unique, so all agents have to learn their expected reward relating to each other.
From an agent's perspective, when considering reward the most important thing about an agent is whether they are a survivor or a zombie, not necessarily which survivor or zombie.
We'd prefer agents learn general policies that consider other agents exchangeable within a team.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/baseline_speed.png}
  \caption{Moving averages for reward and speed in baseline scenario. Survivors in blue and orange.}
  \label{fig:baseline_speed}
\end{figure}

@@

In the \emph{anonymity} scenario we modify the \emph{baseline} scenario to introduce partial observability.
We re-order agents' state vectors each step so that agents within teams are ordered by distance to the observing agent.
To a survivor, a zombie now appears the same as any other zombie, and does not have identity by virtue of index in the state vector.
This reduces the size of the state-space considerably, and allows agents to learn policies that focus on nearby agents.

We expect both survivors and zombies to learn more general policies with faster convergence than the baseline.
We also expect to see zombies chasing which ever survivor is easiest to chase, rather than fixating on a single survivor.
